---
title: "Inverse Gaussian Regressions"
author: "Hugh Rabagliati"
date: "13 June 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
library(fitdistrplus)
library(gamlss)
library(gamlss.dist)
library(lme4)
library(ez)
library(jsonlite)
library(ggplot2)
library(gridExtra)
library(plyr)
library(dplyr)
library(doBy)
library(sn)
Test_Import = function(path_name,expt){
  library(jsonlite)
  
  list.files(path = path_name,full.names = T, pattern = expt) -> file_list
  comp = c()
  for (x in file_list){
    file_name = x
    d <- read.csv(file_name, header = T)
    comp = rbind(comp,d)
    print(x)
  }
  comp$rt <- comp$ReactionTime_column
  comp$Acc <- comp$Valid_column
  comp$SubjNo <- comp$subject_column
  return(comp)
}

```

## Inverse Gaussian Regressions for the Sklar Direct Rep



```{r cars, include=FALSE}
sklar.emo <- Test_Import("./data","sklar_emo")
sklar.emo$Length <- nchar(as.character(sklar.emo$Stim_column))
sklar.emo$Length <- (sklar.emo$Length - mean(sklar.emo$Length))/sd(sklar.emo$Length)

#Mark timeouts as incorrect, for exclusion
sklar.emo[sklar.emo$Acc < 0,]$Acc <- 0

# Remove outlier subjects by Accuracy and RT (mean acc must be > 0.9, mean rt must be > (!!, see by trial exclusion below) 3sd from group mean [ie we remove extra-fast participants)
Acc <- summaryBy(Acc + rt ~ SubjNo, data = sklar.emo, keep.names = T)
sklar.emo <- sklar.emo[sklar.emo$SubjNo %in% Acc[Acc$Acc > 0.9,]$SubjNo,]
sklar.emo <- sklar.emo[sklar.emo$SubjNo %in% Acc[Acc$rt < (mean(Acc$rt) + (3*sd(Acc$rt))),]$SubjNo,]
#Remove incorrect trials
sklar.emo <- sklar.emo[sklar.emo$Acc ==1,]
# Remove RTs +/-3sd from each subject's mean 
sklar.emo <- ddply(sklar.emo, .(SubjNo), function(d){ 
  include = mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt > include[1] & rt < include[2])
})

# Remove RTs < 200ms & > 1000ms
sklar.emo <- subset(sklar.emo, rt > 0.2)
sklar.emo <- subset(sklar.emo, rt <= 10)

# First standardize the MeanAffectivity score
sklar.emo$MeanAffectivity_column <- (sklar.emo$MeanAffectivity_column - mean(sklar.emo$MeanAffectivity_column, na.rm = T))/sd(sklar.emo$MeanAffectivity_column, na.rm = T)

# Lin Reg (sklar style)
sklar.emo$log.rt <- log(sklar.emo$rt)

### sklar sem
sklar.sem <- Test_Import("./data","sklar_sem")
sklar.sem$Length <- nchar(as.character(sklar.sem$Stim_column))
sklar.sem$Length  <- (sklar.sem$Length  - mean(sklar.sem$Length,na.rm= T))/sd(sklar.sem$Length,na.rm= T)
sklar.sem <- sklar.sem[sklar.sem$Type_column != "Sklar_filler",]
sklar.sem$Condition = "Control"
sklar.sem[sklar.sem$Type_column == "Sklar_violation",]$Condition <- "Violation"
sklar.sem$Condition <- as.factor(sklar.sem$Condition)
contrasts(sklar.sem$Condition)[1] <- -1
#Mark timeouts as incorrect, for exclusion
sklar.sem[sklar.sem$Acc < 0,]$Acc <- 0

# Rsemve outlier subjects by Accuracy and RT (mean acc must be > 0.9, mean rt must be > (!!, see by trial exclusion below) 3sd from group mean [ie we rsemve extra-fast participants)
Acc <- summaryBy(Acc + rt ~ SubjNo, data = sklar.sem, keep.names = T)

sklar.sem <- sklar.sem[sklar.sem$SubjNo %in% Acc[Acc$Acc > 0.9,]$SubjNo,]
# Also exclude

sklar.sem <- sklar.sem[sklar.sem$SubjNo %in% Acc[Acc$rt < (mean(Acc$rt) + (3*sd(Acc$rt))),]$SubjNo,]
#Rsemve incorrect trials
sklar.sem <- sklar.sem[sklar.sem$Acc ==1,]

# Rsemve RTs +/-3sd from each subject's mean 
sklar.sem <- ddply(sklar.sem, .(SubjNo), function(d){ 
  include = mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt > include[1] & rt < include[2])
})
# [for Expt 1 only] Remove outliers by condition (less than 3sd from condition mean -- note that this is not a symmetric exclusion criterion)
sklar.sem <- ddply(sklar.sem, .(Condition), function(d){ 
  by_subj_include <- mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt < by_subj_include[2])
})
# Rsemve RTs < 200ms & > 10
sklar.sem <- subset(sklar.sem, rt > 0.2)
sklar.sem <- subset(sklar.sem, rt <= 10)

# Lin Reg (sklar style)
sklar.sem$log.rt <- log(sklar.sem$rt)

# Edin emo
edin.emo <- Test_Import("./data","edin_emo")
edin.emo$Length <- nchar(as.character(edin.emo$Stim_column))
edin.emo$Length <- (edin.emo$Length - mean(edin.emo$Length, na.rm = T))/sd(edin.emo$Length)                                      
#Mark timeouts as incorrect, for exclusion
edin.emo[edin.emo$Acc < 0,]$Acc <- 0
# Remove outlier subjects by Accuracy and RT (mean acc must be > 0.9, mean rt must be > (!!, see by trial exclusion below) 3sd from group mean [ie we remove extra-fast participants)
Acc <- summaryBy(Acc + rt ~ SubjNo, data = edin.emo, keep.names = T)
edin.emo <- edin.emo[edin.emo$SubjNo %in% Acc[Acc$Acc > 0.9,]$SubjNo,]
edin.emo <- edin.emo[edin.emo$SubjNo %in% Acc[Acc$rt < (mean(Acc$rt) + (3*sd(Acc$rt))),]$SubjNo,]
#Remove incorrect trials
edin.emo <- edin.emo[edin.emo$Acc ==1,]
# Remove RTs +/-3sd from each subject's mean 
edin.emo <- ddply(edin.emo, .(SubjNo), function(d){ 
  include = mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt > include[1] & rt < include[2])
})

# Remove RTs < 200ms & > 10s
edin.emo <- subset(edin.emo, rt > 0.2)
edin.emo <- subset(edin.emo, rt <= 10)

# First standardize the MeanAffectivity score
edin.emo$MeanAffectivity_column <- (edin.emo$MeanAffectivity_column - mean(edin.emo$MeanAffectivity_column, na.rm = T))/sd(edin.emo$MeanAffectivity_column, na.rm = T)

contrasts(edin.emo$Type_column)[1] <- -1



# Edin Sem
edin.sem <- Test_Import("./data","edin_sem")
edin.sem$Length <- nchar(as.character(edin.sem$Stim_column))
edin.sem$Length <- (edin.sem$Length - mean(edin.sem$Length))/sd(edin.sem$Length)
edin.sem$Condition = "Violation"
edin.sem[edin.sem$Type_column == "Sensible",]$Condition <- "Control"
edin.sem$Condition <- as.factor(edin.sem$Condition)
contrasts(edin.sem$Condition)[1] <- -1
#Mark timeouts as incorrect, for exclusion
edin.sem[edin.sem$Acc < 0,]$Acc <- 0


# Rsemve outlier subjects by Accuracy and RT (mean acc must be > 0.9, mean rt must be > (!!, see by trial exclusion below) 3sd from group mean [ie we rsemve extra-fast participants)
Acc <- summaryBy(Acc + rt ~ SubjNo, data = edin.sem, keep.names = T)
edin.sem <- edin.sem[edin.sem$SubjNo %in% Acc[Acc$Acc > 0.9,]$SubjNo,]
edin.sem <- edin.sem[edin.sem$SubjNo %in% Acc[Acc$rt < (mean(Acc$rt) + (3*sd(Acc$rt))),]$SubjNo,]
#Rsemve incorrect trials
edin.sem <- edin.sem[edin.sem$Acc ==1,]
# Rsemve RTs +/-3sd from each subject's mean 
edin.sem <- ddply(edin.sem, .(SubjNo), function(d){ 
  include = mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt > include[1] & rt < include[2])
})
# [for Expt 1 only] Remove outliers by condition (less than 3sd from condition mean -- note that this is not a symmetric exclusion criterion)
edin.sem <- ddply(edin.sem, .(Condition), function(d){ 
  by_subj_include <- mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt < by_subj_include[2])
})
# Rsemve RTs < 200ms & > 10
edin.sem <- subset(edin.sem, rt > 0.2)
edin.sem <- subset(edin.sem, rt <= 10)

# Lin Reg (sklar style)
edin.sem$log.rt <- log(edin.sem$rt)
```

## Inverse Gaussian Regressions

GLM Regressions from inverse gaussian famil with log link (seems to converge better). Note that when we include length as a random effect for subjects, model often fails to converge.
```{r GLMs, echo=FALSE}
summary(glmer(rt ~ MeanAffectivity_column+Length + (1+MeanAffectivity_column|SubjNo)+ (1|Stim_column), data = sklar.emo, family = "inverse.gaussian"(link="log")))

summary(glmer(rt ~ Condition+Length + (1+Condition|SubjNo)+ (1|Stim_column), data = sklar.sem, family = "inverse.gaussian"(link="log")))

summary(glmer(rt ~ Type_column+Length + (1+Type_column|SubjNo)+ (1|Stim_column), data = edin.emo, family = "inverse.gaussian"(link="log")))

summary(glmer(rt ~ Condition+Length + (1+Condition|SubjNo)+ (1|Stim_column), data = edin.sem, family = "inverse.gaussian"(link="log")))

```




## Gamma Regressions

GLM Regressions from gamma with inverse link (seems to converge better). Note that when we include length as a random effect for subjects, model often fails to converge. Overall, deviance seems to be higher for Gamma regressions than inverse Gaussian, indicating a worse fit.
```{r GLMs-Gamma, echo=FALSE}
summary(glmer(rt ~ MeanAffectivity_column+Length + (1+MeanAffectivity_column|SubjNo)+ (1|Stim_column), data = sklar.emo, family = "Gamma"))

summary(glmer(rt ~ Condition+Length + (1+Condition|SubjNo)+ (1|Stim_column), data = sklar.sem, family = "Gamma"))

summary(glmer(rt ~ Type_column+Length + (1+Type_column|SubjNo)+ (1|Stim_column), data = edin.emo, family = "Gamma"))

summary(glmer(rt ~ Condition+Length + (1+Condition|SubjNo)+ (1|Stim_column), data = edin.sem, family = "Gamma"))

```


## Standard LM Regressions

```{r LMs-standard, echo=FALSE}
summary(lmer(rt ~ MeanAffectivity_column+Length + (1+MeanAffectivity_column|SubjNo)+ (1|Stim_column), data = sklar.emo, family = "gaussian"(link="log")))

summary(lmer(rt ~ Condition+Length + (1+Condition|SubjNo)+ (1|Stim_column), data = sklar.sem, family = "gaussian"(link="log")))

summary(lmer(rt ~ Type_column+Length + (1+Type_column|SubjNo)+ (1|Stim_column), data = edin.emo, family = "gaussian"(link="log")))

summary(lmer(rt ~ Condition+Length + (1+Condition|SubjNo)+ (1|Stim_column), data = edin.sem, family = "gaussian"(link="log")))

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
