---
title: "Sklar Direct Replication"
author: "Hugh Rabagliati"
date: "9 June 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
library(fitdistrplus)
library(gamlss)
library(gamlss.dist)
library(lme4)
library(ez)
library(jsonlite)
library(ggplot2)
library(gridExtra)
library(plyr)
library(dplyr)
library(doBy)
library(sn)
Test_Import = function(path_name,expt){
  library(jsonlite)
  
  list.files(path = path_name,full.names = T, pattern = expt) -> file_list
  comp = c()
  for (x in file_list){
    file_name = x
    d <- read.csv(file_name, header = T)
    comp = rbind(comp,d)
    print(x)
  }
  comp$rt <- comp$ReactionTime_column
  comp$Acc <- comp$Valid_column
  comp$SubjNo <- comp$subject_column
  return(comp)
}
```

## Sklar's Emotion Experiment


```{r sklar.emo, echo = FALSE, include = FALSE}
sklar.emo <- Test_Import("./data","sklar_emo")
sklar.emo$Length <- nchar(as.character(sklar.emo$Stim_column))
sklar.emo$Length <- (sklar.emo$Length - mean(sklar.emo$Length))/sd(sklar.emo$Length)
#Mark timeouts as incorrect, for exclusion
sklar.emo[sklar.emo$Acc < 0,]$Acc <- 0

# Remove outlier subjects by Accuracy and RT (mean acc must be > 0.9, mean rt must be > (!!, see by trial exclusion below) 3sd from group mean [ie we remove extra-fast participants)
Acc <- summaryBy(Acc + rt ~ SubjNo, data = sklar.emo, keep.names = T)
sklar.emo <- sklar.emo[sklar.emo$SubjNo %in% Acc[Acc$Acc > 0.9,]$SubjNo,]
sklar.emo <- sklar.emo[sklar.emo$SubjNo %in% Acc[Acc$rt < (mean(Acc$rt) + (3*sd(Acc$rt))),]$SubjNo,]
#Remove incorrect trials
sklar.emo <- sklar.emo[sklar.emo$Acc ==1,]
# Remove RTs +/-3sd from each subject's mean 
sklar.emo <- ddply(sklar.emo, .(SubjNo), function(d){ 
  include = mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt > include[1] & rt < include[2])
})

# Remove RTs < 200ms & > 1000ms
sklar.emo <- subset(sklar.emo, rt > 0.2)
sklar.emo <- subset(sklar.emo, rt <= 10)

# First standardize the MeanAffectivity score
sklar.emo$MeanAffectivity_column <- (sklar.emo$MeanAffectivity_column - mean(sklar.emo$MeanAffectivity_column, na.rm = T))/sd(sklar.emo$MeanAffectivity_column, na.rm = T)


```

1. Standard Analyses (rt against mean affective rating)
```{r sklar.emo.analyses, echo=FALSE}
# Lin Reg (sklar style)
sklar.emo$log.rt <- log(sklar.emo$rt)
sklar.emo.sum <- summaryBy(rt + log.rt~ Stim_column + MeanAffectivity_column, data = sklar.emo, keep.names = T)
summary(lm(rt ~ MeanAffectivity_column, data = sklar.emo.sum))
summary(lm(log.rt ~ MeanAffectivity_column, data = sklar.emo.sum))
summary(lmer(rt ~ MeanAffectivity_column + (1+MeanAffectivity_column|SubjNo) + (1|Stim_column), data = sklar.emo))
summary(lmer(log.rt ~ MeanAffectivity_column + (1+MeanAffectivity_column|SubjNo) + (1|Stim_column), data = sklar.emo))
```

And a gamma regression
```{r sklar.emo.Gamma regression}
sklar.emo.sum.raw.gamma <- summary(glmer(rt ~ MeanAffectivity_column+Length + (1+MeanAffectivity_column|SubjNo)+ (1|Stim_column), data = sklar.emo, family = "Gamma"))
print(sklar.emo.sum.raw.gamma)
```


1. Additional Analyses (rt against mean affective rating + length)
```{r sklar.emo.analyses.2, echo=FALSE}
# Lin Reg (sklar style)
sklar.emo$log.rt <- log(sklar.emo$rt)
sklar.emo.sum <- summaryBy(rt + log.rt~ Stim_column + MeanAffectivity_column + Length, data = sklar.emo, keep.names = T)
summary(lm(rt ~ MeanAffectivity_column+Length, data = sklar.emo.sum))
summary(lm(log.rt ~ MeanAffectivity_column+Length, data = sklar.emo.sum))
summary(lmer(rt ~ MeanAffectivity_column + (1+MeanAffectivity_column|SubjNo) + (1|Stim_column), data = sklar.emo))
```

## Sklar's Sensicality Experiment
```{r sklar.sensicality, echo = FALSE, include = FALSE}
sklar.sem <- Test_Import("./data","sklar_sem")
sklar.sem$Length <- nchar(as.character(sklar.sem$Stim_column))
sklar.sem$Length <- (sklar.sem$Length - mean(sklar.sem$Length, na.rm = T))/sd(sklar.sem$Length)
sklar.sem <- sklar.sem[sklar.sem$Type_column != "Sklar_filler",]
sklar.sem$Condition = "Control"
sklar.sem[sklar.sem$Type_column == "Sklar_violation",]$Condition <- "Violation"

#Mark timeouts as incorrect, for exclusion
sklar.sem[sklar.sem$Acc < 0,]$Acc <- 0

# Rsemve outlier subjects by Accuracy and RT (mean acc must be > 0.9, mean rt must be > (!!, see by trial exclusion below) 3sd from group mean [ie we rsemve extra-fast participants)
Acc <- summaryBy(Acc + rt ~ SubjNo, data = sklar.sem, keep.names = T)

sklar.sem <- sklar.sem[sklar.sem$SubjNo %in% Acc[Acc$Acc > 0.9,]$SubjNo,]
# Also exclude

sklar.sem <- sklar.sem[sklar.sem$SubjNo %in% Acc[Acc$rt < (mean(Acc$rt) + (3*sd(Acc$rt))),]$SubjNo,]
#Rsemve incorrect trials
sklar.sem <- sklar.sem[sklar.sem$Acc ==1,]

# Rsemve RTs +/-3sd from each subject's mean 
sklar.sem <- ddply(sklar.sem, .(SubjNo), function(d){ 
  include = mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt > include[1] & rt < include[2])
})
# [for Expt 1 only] Remove outliers by condition (less than 3sd from condition mean -- note that this is not a symmetric exclusion criterion)
sklar.sem <- ddply(sklar.sem, .(Condition), function(d){ 
  by_subj_include <- mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt < by_subj_include[2])
})
# Rsemve RTs < 200ms & > 10
sklar.sem <- subset(sklar.sem, rt > 0.2)
sklar.sem <- subset(sklar.sem, rt <= 10)

# Lin Reg (sklar style)
sklar.sem$log.rt <- log(sklar.sem$rt)
sklar.sem.sum <- summaryBy(rt + log.rt~ SubjNo + Condition, data = sklar.sem, keep.names = T)
```

```{r sklar.sem.analyses, echo = FALSE}
t.test(rt ~ Condition, data = sklar.sem.sum, paired = T)
t.test(log.rt ~ Condition, data = sklar.sem.sum, paired = T)

# lmer (Rabag style)
sklar.sem.sum.raw <- summary(lmer(rt ~ Condition + (1+Condition|SubjNo)+ (1|Stim_column), data = sklar.sem))
print(sklar.sem.sum.raw)
print(paste("p value = ", 2*pnorm(-abs(coef(sklar.sem.sum.raw)[,3]))))

sklar.sem.sum.log <- summary(lmer(log(rt) ~ Condition + (1+Condition|SubjNo)+ (1|Stim_column), data = sklar.sem))
print(sklar.sem.sum.log)
print(paste("p value = ", 2*pnorm(-abs(coef(sklar.sem.sum.log)[,3]))))
```

And a gamma regression
```{r sklar.sem.Gamma regression}
sklar.sem.sum.raw.gamma <- summary(glmer(rt ~ Condition+Length + (1+Condition|SubjNo)+ (1|Stim_column), data = sklar.sem, family = "Gamma"))
print(sklar.sem.sum.raw.gamma)
```



### Now without by condition outlier removal
```{r sklar.sensicality.bycond, echo = FALSE, include = FALSE}
sklar.sem <- Test_Import("./data","sklar_sem")
sklar.sem$Length <- nchar(as.character(sklar.sem$Stim_column))
sklar.sem <- sklar.sem[sklar.sem$Type_column != "Sklar_filler",]
sklar.sem$Condition = "Control"
sklar.sem[sklar.sem$Type_column == "Sklar_violation",]$Condition <- "Violation"

#Mark timeouts as incorrect, for exclusion
sklar.sem[sklar.sem$Acc < 0,]$Acc <- 0

# Rsemve outlier subjects by Accuracy and RT (mean acc must be > 0.9, mean rt must be > (!!, see by trial exclusion below) 3sd from group mean [ie we rsemve extra-fast participants)
Acc <- summaryBy(Acc + rt ~ SubjNo, data = sklar.sem, keep.names = T)

sklar.sem <- sklar.sem[sklar.sem$SubjNo %in% Acc[Acc$Acc > 0.9,]$SubjNo,]
# Also exclude

sklar.sem <- sklar.sem[sklar.sem$SubjNo %in% Acc[Acc$rt < (mean(Acc$rt) + (3*sd(Acc$rt))),]$SubjNo,]
#Rsemve incorrect trials
sklar.sem <- sklar.sem[sklar.sem$Acc ==1,]

# Rsemve RTs +/-3sd from each subject's mean 
sklar.sem <- ddply(sklar.sem, .(SubjNo), function(d){ 
  include = mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt > include[1] & rt < include[2])
})

# Rsemve RTs < 200ms & > 10
sklar.sem <- subset(sklar.sem, rt > 0.2)
sklar.sem <- subset(sklar.sem, rt <= 10)

# Lin Reg (sklar style)
sklar.sem$log.rt <- log(sklar.sem$rt)
sklar.sem.sum <- summaryBy(rt + log.rt~ SubjNo + Condition, data = sklar.sem, keep.names = T)
```

```{r sklar.sem.analyses.bycond, echo = FALSE}
t.test(rt ~ Condition, data = sklar.sem.sum, paired = T)
t.test(log.rt ~ Condition, data = sklar.sem.sum, paired = T)

# lmer (Rabag style)
sklar.sem.sum.raw <- summary(lmer(rt ~ Condition + (1+Condition|SubjNo)+ (1|Stim_column), data = sklar.sem))
print(sklar.sem.sum.raw)
print(paste("p value = ", 2*pnorm(-abs(coef(sklar.sem.sum.raw)[,3]))))

sklar.sem.sum.log <- summary(lmer(log(rt) ~ Condition + (1+Condition|SubjNo)+ (1|Stim_column), data = sklar.sem))
print(sklar.sem.sum.log)
print(paste("p value = ", 2*pnorm(-abs(coef(sklar.sem.sum.log)[,3]))))
```

## Edinburgh Emotion Expt

```{r edin.emo.expt, echo = FALSE, include=FALSE}
#############
# Edinburgh Emo Expt

edin.emo <- Test_Import("./data","edin_emo")
edin.emo$Length <- nchar(as.character(edin.emo$Stim_column))
edin.emo$Length <- (edin.emo$Length - mean(edin.emo$Length, na.rm = T))/sd(edin.emo$Length)
#Mark timeouts as incorrect, for exclusion
edin.emo[edin.emo$Acc < 0,]$Acc <- 0
# Remove outlier subjects by Accuracy and RT (mean acc must be > 0.9, mean rt must be > (!!, see by trial exclusion below) 3sd from group mean [ie we remove extra-fast participants)
Acc <- summaryBy(Acc + rt ~ SubjNo, data = edin.emo, keep.names = T)
edin.emo <- edin.emo[edin.emo$SubjNo %in% Acc[Acc$Acc > 0.9,]$SubjNo,]
edin.emo <- edin.emo[edin.emo$SubjNo %in% Acc[Acc$rt < (mean(Acc$rt) + (3*sd(Acc$rt))),]$SubjNo,]
#Remove incorrect trials
edin.emo <- edin.emo[edin.emo$Acc ==1,]
# Remove RTs +/-3sd from each subject's mean 
edin.emo <- ddply(edin.emo, .(SubjNo), function(d){ 
  include = mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt > include[1] & rt < include[2])
})

# Remove RTs < 200ms & > 10s
edin.emo <- subset(edin.emo, rt > 0.2)
edin.emo <- subset(edin.emo, rt <= 10)

# First standardize the MeanAffectivity score
edin.emo$MeanAffectivity_column <- (edin.emo$MeanAffectivity_column - mean(edin.emo$MeanAffectivity_column, na.rm = T))/sd(edin.emo$MeanAffectivity_column, na.rm = T)

```
```{r edin.emo.expt.analyses, echo = FALSE}

# Lin Reg (edin style)
edin.emo$log.rt <- log(edin.emo$rt)
edin.emo.sum <- summaryBy(rt + log.rt~ Stim_column + MeanAffectivity_column, data = edin.emo, keep.names = T)
summary(lm(rt ~ MeanAffectivity_column, data = edin.emo.sum))
summary(lm(log.rt ~ MeanAffectivity_column, data = edin.emo.sum))

# Lin Reg (sklar style)
edin.emo$log.rt <- log(edin.emo$rt)
edin.emo.sum.factorial <- summaryBy(rt + log.rt ~ SubjNo + Type_column, data = edin.emo, keep.names = T)
t.test(rt ~ Type_column, data = edin.emo.sum.factorial, paired = T)
t.test(log.rt ~ Type_column, data = edin.emo.sum.factorial, paired = T)

# lmer (Rabag style)
edin.emo.sum.raw <- summary(lmer(rt ~ Type_column+Length + (1+Type_column|SubjNo)+ (1|Stim_column), data = edin.emo))
print(edin.emo.sum.raw)
print(paste("p value = ", 2*pnorm(-abs(coef(edin.emo.sum.raw)[,3]))))

edin.emo.sum.log <- summary(lmer(log.rt ~ Type_column + (1+Type_column|SubjNo)+ (1|Stim_column), data = edin.emo))
print(edin.emo.sum.log)
print(paste("p value = ", 2*pnorm(-abs(coef(edin.emo.sum.log)[,3]))))
```
And a gamma regression
```{r edin.emo.gamme, echo=FALSE}
edin.emo.sum.raw.gamma <- summary(glmer(rt ~ Type_column+Length + (1+Type_column|SubjNo)+ (1|Stim_column), data = edin.emo, family = "Gamma"))
print(edin.emo.sum.raw.gamma)

```

## Edinburgh Semantics Experiment
```{r edin.sem.data, echo=FALSE, include=FALSE}
# Edin Sem
edin.sem <- Test_Import("./data","edin_sem")
edin.sem$Length <- nchar(as.character(edin.sem$Stim_column))
edin.sem$Length <- (edin.sem$Length - mean(edin.sem$Length))/sd(edin.sem$Length)
edin.sem$Condition = "Violation"
edin.sem[edin.sem$Type_column == "Sensible",]$Condition <- "Control"

#Mark timeouts as incorrect, for exclusion
edin.sem[edin.sem$Acc < 0,]$Acc <- 0


# Rsemve outlier subjects by Accuracy and RT (mean acc must be > 0.9, mean rt must be > (!!, see by trial exclusion below) 3sd from group mean [ie we rsemve extra-fast participants)
Acc <- summaryBy(Acc + rt ~ SubjNo, data = edin.sem, keep.names = T)
edin.sem <- edin.sem[edin.sem$SubjNo %in% Acc[Acc$Acc > 0.9,]$SubjNo,]
edin.sem <- edin.sem[edin.sem$SubjNo %in% Acc[Acc$rt < (mean(Acc$rt) + (3*sd(Acc$rt))),]$SubjNo,]
#Rsemve incorrect trials
edin.sem <- edin.sem[edin.sem$Acc ==1,]
# Rsemve RTs +/-3sd from each subject's mean 
edin.sem <- ddply(edin.sem, .(SubjNo), function(d){ 
  include = mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt > include[1] & rt < include[2])
})
# [for Expt 1 only] Remove outliers by condition (less than 3sd from condition mean -- note that this is not a symmetric exclusion criterion)
edin.sem <- ddply(edin.sem, .(Condition), function(d){ 
  by_subj_include <- mean(d$rt, na.rm = T) + 3*c(-1,1)*sd(d$rt,na.rm = T)
  d = subset(d, rt < by_subj_include[2])
})
# Rsemve RTs < 200ms & > 10
edin.sem <- subset(edin.sem, rt > 0.2)
edin.sem <- subset(edin.sem, rt <= 10)

```

``` {r edin.sem.analyses, echo = FALSE}
# Lin Reg (sklar style)
edin.sem$log.rt <- log(edin.sem$rt)
edin.sem.sum <- summaryBy(rt + log.rt ~ SubjNo + Condition, data = edin.sem, keep.names = T)
t.test(rt ~ Condition, data = edin.sem.sum, paired = T)
t.test(log.rt ~ Condition, data = edin.sem.sum, paired = T)

# lmer (Rabag style)
edin.sem.sum.raw <- summary(lmer(rt ~ Condition+Length + (1+Condition|SubjNo)+ (1|Stim_column), data = edin.sem))
print(edin.sem.sum.raw)
print(paste("p value = ", 2*pnorm(-abs(coef(edin.sem.sum.raw)[,3]))))

edin.sem.sum.log <- summary(lmer(log.rt ~ Condition + (1+Condition|SubjNo)+ (1|Stim_column), data = edin.sem))
print(edin.sem.sum.log)
print(paste("p value = ", 2*pnorm(-abs(coef(edin.sem.sum.log)[,3]))))

```
And a gamma regression
```{r edin.sem.gamma, echo=FALSE}
edin.sem.sum.raw.gamma <- summary(glmer(rt ~ Condition+Length + (1+Condition|SubjNo)+ (1|Stim_column), data = edin.sem, family = "Gamma"))
print(edin.sem.sum.raw.gamma)

```